
```{r}
#| setup: true
#| echo: false
#| include: false

library(socmod)
```


# Diffusion

<br>

In the context of sustainability and climate adaptation, behavior change often
depends not only on individual decisions but also on social networks that
constrain who interacts with whom, and whether individuals use adaptive social
learning to choose behaviors, as opposed to mindless, probabilistic adoption of
new behaviors. When individuals use adaptive social learning to choose between
behaviors, this provides the selection mechanism that generates cultural
evolution. 

<br>


## Introduction

The puzzles of diffusion and belief change provide resistance to spreading
sustainable practices unless they are addressed. Today a Cambrian explosion in
green tech startups and new products and data analytics continues continues.
Ancient Indigenous practices have helped humans adapt to climate change for
generations upon generations. Unfortunately these practices are ignored in favor
of expensive, poorly tested, maladaptive "grey infrastructure", like sea walls
that act more like dams once breached and soak up humanitarian aid like a money
sponge. Similarly, In this chapter we build up models of social diffusion via
social learning, starting from a minimal specification of how social interaction
and learning work. Specifically, we start with the *Unconstrained Contagion*
model of stochastic transmission in a very large population, so new learners of
sustainable practices are always available. In this chapter we only consider
behaviors that individuals do alone gain benefit. However, the material in this
chapter provides the foundation for the next two chapters. 

In the next two chapters, we extend the models developed here to understand the
diffusion of behaviors that yield benefits or payoffs only in *coordination*
with others doing either *cooperative* (i.e., the same) or *complementary*
(i.e., different) behaviors.  Promoting the diffusion of cooperation could
improve the success rate of natural resource conservation interventions, such as
sustainable groundwater usage cooperation to avoid exhausting underground
aquifers that people and farms depend on. In the second chapter, we use
leader-follower decisions between men and women as a model for how negative
social judgements against men who follow women could support despite progress
towards gender pay equity, more maternal leave, and other material improvements. 


## Overview

In this chapter we start building our framework for social diffusion, represented by mechanistic mathematical and software models of social transmission and learning. We begin with a simple model of a chain of unconstrained social transmission starting from a single teacher, with no limit on how many people might learn from teachers of teachers of teachers, and so on. We also assume behaviors do not require coordination with others, and so the benefit of doing a behavior is independent of the number of people doing the behavior. I show how we can use discrete-time difference equations, continuous-time differential equations, or agent-based simulation to arrive at the same conclusion: prevalence increases exponentially over time under these assumption. We tag this the *Going Viral* model as it could represent the "going viral" stage of an emerging trend when there are many potential new adopters and few current adopters [@Rogers2003;@Smaldino2023_Ch4Contagion].

To understand how real-world constraints affect diffusion, we scaffold from this
unconstrained *Going Viral* model, adding constraints one at a time and
observing their effects.  First is the constraint of *finite populations* in the
section *Bounded Virality* below. If we had more time together, the next section
would  been is the *Viral Friends* section where we consider the effect of interaction structure, which could be represented by homophily or a social network, for example. Finally,
adaptive social learning constrains diffusion to cultural evolutionary dynamics, presented in the section *Guided Virality*. 

One side effect of this organization is that cultural evolution is revealed as  diffusion process. Cultural evolution is enabled and driven by adaptive social learning, which provides selection pressure on behaviors [@Richerson2020]. *Behavior* is the analogue of *phenotype* in genetic evolution; *adaptive social learning* is the analogue of *preferential mating* in genetic evolution [@CavalliFeldman1981;@Boyd1995;@BoydRicherson2005]. In both cases, the *behavioral gambit* and *phenotypic gambit* are common names for the modeling assumption that knowledge of how to do a behavior, or the genetic encoding for the pheotype, are faithfully transmitted. Furthermore, this *gambit* assumes that once an individual knows how to do a behavior, they perform it perfectly, or the individual's genotype is perfectly expressed in the phenotype. A final assumption embedded in this gambit is a one-to-one correspondence between knowledge/genetics and behavior/phenotype. 

In *adaptive social learning*, model individuals prefer learning from others who are more successful, for example, or perhaps prefer adopting behaviors practiced by a greater number of their social partners [@Laland2004;@Kendal2018;@Toyokawa2019]. If individual psychology is such that more successful individuals are more likely to be chosen as teachers, this is called *success-biased learning*. When more prevalent behaviors are preferentially learned, this is *frequency-biased learning*. Keep in mind that these adaptive learning strategies are to cultural evolution what
preferential mating is to genetic evolution: adaptive social learning induces
evolutionary diffusion dynamics. 

In the two chapters following this one we will harness cultural evolution to
understand how norms of cooperation and gender equity in leadership could evolve to sticky equilibria that may take special efforts to deconstruct, even in idealized simulations. These models are the final scaffold on the diffusion model presented here. We represent these coordination problems in sustainability in terms of *evolutionary game theory*. 


## These models not endorsed for belief/opinion change

Social influence dynamics of beliefs or opinions [@Blau1974;@DeGroot1974;@Lorenz2007;@Flache2011;@Turner2018;@Galesic2021] are
considered as a different class of models in this framework since the thing being transmitted is *latent*, i.e., not directly observable. In these cases, we can only observe *behaviors* that either report or belie latent psychological beliefs or opinions. This is planned for future incorporation into the Computational Social Science for Sustainability course material in the near future.


## Model

The abstract model of diffusion presented here provides a formal and
agent-based framework to be filled in with specific social structure and 
socio-cognitive processes as appropriate for different contexts. Contexts are
specified by, for example, 
the available behaviors, social network structure, and dominant social
learning process, e.g., contagion, success-biased, and conformity. 

We begin by developing a formal modeling system for behavior diffusion that 
can be used for a number of applications. An evolutionary dynamical systems model that
assumes a large (i.e., $N \to \infty$), well-mixed population time series of 
behavioral adoption can generate time series and be used for *invasion analyses*
that can provide simple heuristics for understanding how well different learning
strategies can promote self-sustaining behavioral diffusion following a
sustainability intervention. This diffusion model model is formed by
manipulating the replicator equation to be expressed in terms of state
transitions. As part of our Analysis section below, 
I will prove that conformity alone cannot 
stimulate self-sustaining behavior diffusion when the behavior is initially
rare, as is the case currently for truly adaptive, sustainable practices. 
On the other hand, I will also show that
success-biased social learning can be harnessed to stimulate faster spread of
sustainable adaptations.

These state transition probabilities naturally slot in to the
Kimura-Crow model of trait diffusion under replicator-like dynamics, but with
stochastic dynamics among finite populations. This approach can be used to
generate time series of adaptation prevalence, but for our analyses we use 
another useful feature of this model: its ability to calculate the *success
rate* of an intervention, i.e., the probability that all individuals adopt the
adaptive sustainable practice, $A$.
This is commonly known as the *fixation probability* of a trait 
in theoretical biology.

Agent-based modeling is a computational technique that explicitly specifies
cognitive attributes and rules that *agents*, i.e., simulated people follow.
I will close this section demonstrating how to develop agent-based models that
use different learning rules, social networks, and other model dynamics that
mechanistically represent the identical behavior change transition
probabilities. For this we will use my R library for agent-based modeling,
[`socmod`](https://github.com/CSS4S/socmod). Social scientists can
write code that describes how learning works, and who interacts with whom.
Formal models help us understand the quantitative implications of our verbal
models at the most basic level, often with the most unrealistic assumptions
that still prove useful. Agent-based models complement more abstract formal
mathematical models by providing scientists with a way to model detail on
finer scales and test how additional factors like group structure and social
networks affect diffusion.

Our models generate both *observations* of prevalence time series and *outcomes*
of whether a simulated intervention is *successful*. In addition to these, we
will analyze the *onset dynamics* that tell us whether the adaptive behavior
will endogenously diffuse. In other words, onset dynamics tell us whether 
the adaptive behavior will continue to diffuse sociall following direct
instruction of the seed set of individuals who participated in the intervention. 
These analyses will be explained in further detail as needed in the Analysis
following the model exposition.


### The Prevalence Dynamic

The *prevalence* of a behavior is the fraction of a population that has
adopted that behavior. The prevalence of adaptive behavior
$A$ at time $t$ is denoted $a_t$ if we are considering discrete time, where
the time between one time step and another is one, i.e., $\Delta t = 1$. In
computational science, $\Delta$ to the left of another variable means *change
in*. 

The *prevalence dynamic* for behavior diffusion with two options represents the change in $a$
over one time step. For discrete time, the change in prevalence, $\Delta a_t$,
over one time step, $\Delta t = 1$, is
\newcommand{\pal}{P(A \mid L)}
\newcommand{\pla}{P(L \mid A)}
$$
\frac{\Delta a_t}{\Delta t}  = \Delta a_t = (1 - a_t)\pal + a_t~\pla.
$$
In words this says that the change in $a$ *increases* by the chance that an
$L$-doer changes to be an $A$-doer, scaled by the prevalence of $L$-doers in the
population, which is $1 - a$. The 

We can do a mathematical trick where we let the change in time get very small,
written as an arrow point towards, or "going to", zero: $\Delta t \to 0$. Then
instead of writing $\Delta t$ we write the change as $dt$, where the letter *d*
stands in for the symbol indicating change, but now a *small* one. If time
changes very little for every iteration of the model, then prevalence changes
very little, too. Then we have that $\Delta a \to da$ as well. This brings us
from a discrete to a continuous model, and now we can use calculus to understand
how different socio-cognitive mechanisms and processes affect whether prevalence
dynamics lead to widespread diffusion. In this case, we drop the subscript $t$
on prevalence, and hide the $(t)$ part of the continuous prevalence $a(t)$
so that the prevalence dynamic becomes
\newcommand{\dadt}{\frac{da}{dt}}
$$
\dadt = \dot a =  (1 - a)\pal + a\pla.
$$


### Going Viral: Contagion

The contagion model of social transmission make minimal assumptions, but still enable helpful analyses. We fill in $\pal$ and $\pla$ in the prevalence dynamic as follows. In contagion, $L$-doers switch behavior and adopt $A$ with some chance, $\alpha$, when they interact with an $A$-doer. The second assumption is that $A$-doers sometimes can not or do not continue doing the adaptive behavior, and *drop* it with probability $\delta$. Dropping an adaptation could be incidental, for example if someone had installed residential solar at one home, but they are moving somewhere else that doesn't have residential solar, and so will have to stop doing the behavior *generate home electricity with solar energy*, at least for some time. It could also be due to forgetting, changing preferences, or any other possible explanation.

We represent contagion assumptions in $\pal$ and $\pla$ as
$$
\pal = \alpha a, \quad \pla = \delta.
$$
Then the full prevalence dynamics are

\newcommand{\adot}{\dot a}
$$
\adot = \alpha a(1 - a) - \delta a
$$


#### Prevalence dyanmics {.unnumbered}

The discrete model can be represented as the following function that takes variables corresponding to time, `t`, an adoption rate, `adopt_rate`, and the drop rate, `drop_rate`, 
which are $t$, $\alpha$, and $\delta$ in math. 
```{r}
a <- function(t, adopt_rate = 0.2, drop_rate = 0.1, a_0 = 1) {
  rho <- adopt_rate - drop_rate
  a_ret <- a_0 * exp(rho * t)
  return (a_ret)
}
```

I will now create a table of values for $n(t)$ for different adoption rates,
$\alpha \in \{0.1, 0.105, 0.2, 0.5\}$, all with the same drop rate, $\delta = 0.1$.
I'll make a function to encapsulate the boilerplate steps called `make_a_tbl`
in the code block below (unfold to view). It uses some helpful default settings
to make an interesting visualization, which we do below. Below is the function
signature for `make_a_tbl`, with the full function definition provided in a folded code block below that. Click the triangle to unfold the full definition. 

$$
\dadt = \dot a = 
$$


```{r}
#| eval: false
make_a_tbl <- function(tmin = 0.0, tmax = 20.0, dt = 0.2, 
                       adopt_rates = seq(0.1, 0.2, 0.025), drop_rate = 0.05) 
```

```{r}
#| code-fold: true
#| code-summary: "`make_a_tbl` function definition"
make_a_tbl <- function(tmin = 0.0, tmax = 20.0, dt = 0.2, 
                       adopt_rates = seq(0.1, 0.2, 0.025), drop_rate = 0.05) {
  
  # Define vector of time points passed to the n function defined above
  tvec <- seq(tmin, tmax, dt)
  
  # Create table to plot a_t for different adoption rate (alpha) values
  a_tbl <- tibble::tibble(
    # Repeat time vector four times for each alpha.
    t = rep(tvec, length(adopt_rates)),  
    
    # Create a_t vector for each adopt_rate, a_0=1 implicit
    a_t = 
      purrr::map(adopt_rates, ~ a(tvec, .x, drop_rate)) |> 
      purrr::flatten_dbl(),
    
    # Repeat adopt rate for each tstep
    adopt_rate = factor(
      purrr::map(adopt_rates, ~ rep(.x, length(tvec))) |> 
      purrr::flatten_dbl(),
      levels = adopt_rates
    )
  )
  
  return (a_tbl)
}
```

Now let's use `ggplot2` to plot the series for each adoption rate, which will
be indicated by line color and type. 

```{r}
library(ggplot2)
a_tbl <- make_a_tbl()
unconstrained_plot <- ggplot(a_tbl, aes(x = t, y = a_t, 
                       color = adopt_rate, 
                       linetype=adopt_rate)) +
  geom_line(linewidth = 1.2) + theme_classic(base_size = 12)
print(unconstrained_plot)
```


#### Check discrete and continuous are equivalent {.unnumbered}

Let's close our analysis by checking that $a_t = \lambda^t a_0$ generates
equivalent values of $n(t')$ for integer values $t'=0,1,2,\ldots,T$. To do this
we'll create another `make_` function but for the discrete formula for $a_t$ 
(Equation 2). We'll then (literally) add those points 
to the `unconstrained_plot`, coloring by adoption rate. 

In the code block below we write an R function for $a_t$, `a_t_discrete`, which
is used by `make_a_discrete_tbl` to create a table of discrete-model values from
time steps 0 to 20, this time setting `dt = 1`. The function signatures are below. Expand the code block below that to see the full function definitions.
```{r}
#| eval: false
a_t_discrete <- function(t, adopt_rate = 0.2, drop_rate = 0.1, a_0 = 1)
make_a_discrete_tbl <- function(tmin = 0L, tmax = 20L,  
                                adopt_rates = seq(0.1, 0.2, 0.025), 
                                drop_rate = 0.05)
```

```{r}
#| code-fold: true
#| code-summary: "`make_a_discrete_tbl` function definition"
a_t_discrete <- function(t, adopt_rate = 0.2, drop_rate = 0.1, a_0 = 1) { 
  lambda <- (1 + adopt_rate - drop_rate)
  a_t <- a_0 * (lambda ** t)
  return (a_t)
}
make_a_discrete_tbl <- function(tmin = 0L, tmax = 20L,  
                                adopt_rates = seq(0.1, 0.2, 0.025), 
                                drop_rate = 0.05) {
  
  # Define vector of time points passed to the n function defined above
  tvec <- tmin:tmax
  
  # Create table to plot a_t for different adoption rate (alpha) values
  a_tbl <- tibble::tibble(
    # Repeat time vector four times for each alpha.
    t = rep(tvec, length(adopt_rates)),  
    
    # Create a_t vector for each adopt_rate, a_0=1 implicit
    a_t = 
      purrr::map(adopt_rates, ~ a(tvec, .x, drop_rate)) |> 
      purrr::flatten_dbl(),
    
    # Repeat adopt rate for each tstep
    adopt_rate = factor(
      purrr::map(adopt_rates, ~ rep(.x, length(tvec))) |> 
      purrr::flatten_dbl(),
      levels = adopt_rates
    )
  )
  
  return (a_tbl)
}

```

```{r}
a_discrete_tbl <- make_a_discrete_tbl()
head(a_discrete_tbl, n = 20)
```
Plot objects returned by `ggplot2` can be extended. In this case we add points for the discrete time steps, expecting they will line up with the lines plotted above.
```{r}
unconstrained_plot_update <- unconstrained_plot + 
  geom_point(aes(x = t, y = a_t), data = a_discrete_tbl, size = 4, alpha = 0.8)
print(unconstrained_plot_update)
```

Success!


<br>


### Guided Virality: Cultural Evolution

Cultural evolution has provided many explanations for previously mysterious
phenomena, such as cultural ratcheting \cite{Garland2022,Andersson2016}, identity signaling, the evolution of bad
science [@Smaldino2016NatSel;@Smaldino2019], and more. Its power comes from its  formulation of human populations as a system of replicators who pass on their "trait"
to their "offspring". However, as time has progressed, we can see that previous formulations perhaps overcomplicated the situation by assuming that the locus of the *cultural selection* process is preferential mating, resulting in Punnet-square style pairings of diploid *alleles* that stand in for *behaviors* in the classic formulation [@CavalliFeldman1981]. One additional hidden assumption powers the use of classic genetic evolution and cultural evolution alike: the *phenotypic gambit* in genetic evolution assumes that an individual's phenotype (e.g., an expressed trait $A$) is a suitable stand-in for the genetic material, the *allele*. In our model we make a similar, but distinct, assumption. When we say a behavior is transmitted, this includes acquiring the necessary skills to do the behavior. The learning process itself is abstracted away in basic models of cultural evolution like this one.

To show that the prevalence dynamic can represent cultural evolution, we show it is actually equivalent to the *replicator equation* first, without mutation. We exclude mutation because in most cases there already are sustainable practices we could be doing more, but they haven't diffused widely. Some Indigenous sustainable practices have existed for millenia, like mangrove forest management for mitigating sea inundation [@McNamara2020;@Piggott-McKellar2020] and prescribed burns to mitigate the risk of catastrophic fire [@Eisenberg2019;@Kolden2019]. Our focus is endogenous dynamics, so mutation could be ignored for strategic reasons as well. 


$$
\frac{da}{dt} = a(w_A - \bar{w})
$$

where:

- $a$: frequency of type $A $
- $w_A$: differential reproduction rate of type $A $
- $\bar{w} = a w_A + (1 - a) w_L$: average reproduction rate

This isn’t about imitation — it models how types spread when some individuals leave more offspring than others.

In cultural evolution, though, traits spread through **learning**, not reproduction. So we reinterpret this equation using **behavioral transitions** instead.

We now show how the replicator equation can be re-expressed in terms of individual-level transitions:

Start from:
$$
\frac{da}{dt} = a(w_A - \bar{w})
$$

Substitute $\bar{w} = a w_A + (1 - a) w_L$:
$$
\frac{da}{dt} = a(w_A - a w_A - (1 - a) w_L) = a(1 - a)(w_A - w_L)
$$

Now divide and multiply by $\bar{w}$:
$$
\frac{da}{dt} = \frac{a(1 - a)}{\bar{w}}(w_A - w_L) \cdot \bar{w}
$$

Define:
$$
P(A \mid L) = \frac{a w_A}{\bar{w}}, \quad P(L \mid A) = \frac{(1 - a) w_L}{\bar{w}}
$$

Then:
$$
\frac{da}{dt} = (1 - a) P(A \mid L) - a P(L \mid A)
$$

#### Success-Biased Learning

Learners using the success-biased strategy preferentially select teachers with greater apparent fitness. In our models fitness values are the same for every behavior for every agent. We call $f_A$ the  from doing the behavior $A$, the adaptive behavior. Similarly, $f_L$ is the fitness gained from doing the legacy behavior, $L$. 

We now formalize the success-biased learning model by writing equations for $P(A|L)$ and $P(L|A)$ based on their verbal description [@Smaldino2020d]. For someone currently doing $L$, the chance they will adopt practice $A$ instead is proportional to the prevalence of $A$, $a$, and the fitness of those doing that behavior, $f_A$. 
$$
P(A \mid L) \propto a f_A.
$$

Similarly, if one is doing $A$, the chance they will adopt $L$ instead is proportional to
$$
P(L \mid A) \propto (1 - a) f_L
$$

We need to normalize by the sum of the probabilities since these must sum to 1. This sum happens to be the mean 
$$
\bar{f} = a f_A + (1 - a) f_L.
$$

This gives:

$$
\frac{da}{dt} = \frac{a(1 - a)}{\bar{f}} (w_A - w_L)
$$


#### Frequency-Biased Learning

We then modeled **frequency bias** using an exponent $\gamma = \log \kappa$, giving:

\newcommand{\apg}{a^{1+\gamma}}
\newcommand{\mapg}{(1 - a)^{1 + \gamma}}
$$
P(A) = \frac{\apg}{\apg + \mapg}
$$

If everyone copies in proportion to frequency, then:

$$
\frac{da}{dt} = P(A) - a = \frac{a^\gamma}{a^\gamma + (1 - a)^\gamma} - a
$$

We also simplified this to a symmetric form:

$$
\frac{da}{dt} = \frac{a^\gamma(1 - a) - a(1 - a)^\gamma}{a^\gamma + (1 - a)^\gamma}
$$



#### Onset dynamics

To analyze behavior near $a = 0$, we expanded:

- $a^\gamma \approx 0$
- $(1 - a)^\gamma \approx 1 - \gamma a + \frac{\gamma(\gamma - 1)}{2} a^2 - \frac{\gamma(\gamma - 1)(\gamma - 2)}{6} a^3 + \dots$

Then:

**Numerator**:
$$
-a + \gamma a^2 - \frac{\gamma(\gamma - 1)}{2} a^3
$$

**Denominator**:
$$
1 - \gamma a + \frac{\gamma(\gamma - 1)}{2} a^2
$$

So:

$$
\frac{da}{dt} \approx -a + \gamma a^2 - \left(\frac{\gamma(\gamma - 1)}{2} + \gamma^2\right) a^3 + \mathcal{O}(a^4)
$$

This shows that:
- For **any finite $\gamma $**, $\frac{da}{dt} < 0 $near $a = 0 $
- Only in the limit $\gamma \to -\infty$ (strong anti-conformity) does $\frac{da}{dt} > 0$ near zero

---

#### The Anti-Conformity Paradox

- **Anti-conformity enables invasion but prevents retention**
- **Anti-conformity is still weaker than **
- **Conformity enables retention but blocks invasion**

So frequency bias alone cannot explain the emergence and spread of adaptive behaviors. Other forces (e.g. success bias, drift, coordination) are required.


#### Broader Implication {.unnumbered}

This framework — based on transition probabilities — unifies:
- Success bias
- Frequency bias
- Replicator dynamics
- Epidemic-style (SIS) models

And it reveals a core result: **conformity blocks innovation**, while **anti-conformity can never sustain it**.

These dynamics can also be tuned developmentally, suggesting new bridges to psychology and life-history theory.




#### Dynamics {.unnumbered}

When $t$ is continuous we can write the number of adopters of $A$ as a mathematical function of time with $t$ in parentheses: $n(t)$. Instead of a recursion equation:

$$
\frac{da}{dt} = \alpha a - \delta a
$$

Which integrates to:
$$
a(t) = a_0 a^{\rho t},
$$
where $\rho = \alpha - \delta$. 

If we restrict $t$ to integers, i.e., $t \in \{0, 1, \ldots, T\}$, then:
$$
a(t) = \{a_0, a_0 \cdot e^{\rho}, a_0 \cdot e^{2\rho}, \ldots, a_0 \cdot e^{T\rho}\}.
$$

This implies that $e^\rho = \lambda$, so:
$$
\rho = \ln \lambda.
$$

We can verify this algebraically. If:
$$
a_0 e^{t'\rho} = a_0 \lambda^{t'},
$$
then dividing both sides by $a_0$ and taking the natural logarithm gives:
$$
\ln e^{t'\rho} = \ln \lambda^{t'},
$$
and using the identity $\log_b(x^y) = y \log_b(x)$:
$$
t' \ln e^\rho = t' \ln \lambda.
$$

Dividing both sides by $t'$ and noting that $\ln e^\rho = \rho$, we confirm:
$$
\rho = \ln \lambda,
$$
visualized in the Figure below.


## Discussion

The social diffusion of sustainable practices, or any behavior, occurs through
social learning between individuals over time. 
If there are many who have not yet adopted some practice and that practice is
more likely to to be adopted than dropped, the spread of that practice will
seem like it will forever accelerate. However, when a significant 
proportion of individuals in a population begin to adopt the behavior, the
number of potential learners decreases and the change in adaptive behavior
prevalence over time begins to decrease. The replicator equation, the
cornerstone of evolutionary theory, can be written as a state transition
equation, where state transition probabilities correspond to different
learning processes. This includes contagion learning. This implies that
contagion learning is a special case of the replicator dynamic, which further
implies that contagion learning is a special case of cultural evolution,
generally construed. 

I proved that this that conformity alone cannot diffuse an adaptation.
Smaldino (2018) says "sigmoid curves are good indicators of conformist
transmission", but this seems to imply that conformist transmission alone
cannot possibly generate a sigmoid curve. Since we can obtain contagion
diffusion dynamics from the replicator equation, but not vice-versa, this
tells us that a sigmoidal prevalence time series alone cannot tell us much
beyond some sort of replicator is at work. 
The evolutionary replicator dynamic, then, was shown to be equivalent to a state
transition dynamic, including contagion transmission. 
The behavior switching probabilities provide an abstract
process to be filled in and customized for specific investigations. This
unlocks the power of invasion analysis for a larger class of learning
processes that don't necessarily neatly map onto concepts of *fitness* and
*reproduction*, but do specify under what conditions one individual doing one
behavior may adopt the alternative behavior. From this we 
- This conceptualization generates some new questions whose answers could
further serve the cause of promoting sustainability through intelligent
intervention design. First, it provides a method for formal analysis of invasion
dynamics with highly non-linear differential equations. It seems plausible
that complex contagion, prestige bias, and social network constraints could be
expressed in this framework. Then one simply expands the derivative around 
$a << 1$ and calculates the sign, as we did to prove conformity cannot diffuse
adaptations.
